Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-24 manuscript/draft.Rmd
typos

Three of models used in this study were fit to each site separately, with no
environmental information (Table 1). These models were fit to each BBS route
twice: once using the residuals from the observer model, and once using the raw
richness values. When correcting for observer effects, we averaged across 500
models that were fit separately to the 500 Monte Carlo estimates of the observer
effects, to account for our uncertainty in the true values of those effects. All
of these models use a Gaussian error distribution (rather than a count
distribution) for reasons discussed below (see "Model evaluation").

@@

One of the main alternatives to stacked SDMs is modeling richness directly using
environmental variables and using the resulting models to make forecasts. Two
studied compared the SDM and direct richness modeling approaches, and reported
that the methods yielded equivalent results for forecasting diversity
[@algar2009; @distler2015]. While our results generally support the idea of
rough equivalence between stacked SDMs and direct richness modeling for point
estimates, they also show that stacked SDMs dramatically understimate the
uncertainty. For this reason, direct modeling of richness is a better overall
approach to forecasting richness. A similar result is seen when comparing joint
species distribution models (JSDMs) to stacked single species distribution
models. For point estimates, the joint distribution models are roughly
equivalent to stacked SDMs, but the JSDMs provide much better estimates of
uncertainty [@harris2015; @warton2015]. In fact, JSDMs and direct richness modeling
provide some of the best estimates of uncertainty across all modeling
approaches. This highlights the importance of evaluating models based on their
uncertainty as well as their mean estimates (Box 1). Not doing so is
particularly problematic in this case, because the summed species distribution
models are overly confident, which means that these models could mislead
ecologists into believing that richness would be restricted to a much narrower
range than would actually occur.

>>>>

Three of the models used in this study were fit to each site separately, with no
environmental information (Table 1). These models were fit to each BBS route
twice: once using the residuals from the observer model, and once using the raw
richness values. When correcting for observer effects, we averaged across 500
models that were fit separately to the 500 Monte Carlo estimates of the observer
effects, to account for our uncertainty in the true values of those effects. All
of these models use a Gaussian error distribution (rather than a count
distribution) for reasons discussed below (see "Model evaluation").

@@

One of the main alternatives to stacked SDMs is modeling richness directly using
environmental variables and using the resulting models to make forecasts. Two
studies compared the SDM and direct richness modeling approaches, and reported
that the methods yielded equivalent results for forecasting diversity
[@algar2009; @distler2015]. While our results generally support the idea of
rough equivalence between stacked SDMs and direct richness modeling for point
estimates, they also show that stacked SDMs dramatically understimate the
uncertainty. For this reason, direct modeling of richness is a better overall
approach to forecasting richness. A similar result is seen when comparing joint
species distribution models (JSDMs) to stacked single species distribution
models. For point estimates, the joint distribution models are roughly
equivalent to stacked SDMs, but the JSDMs provide much better estimates of
uncertainty [@harris2015; @warton2015]. In fact, JSDMs and direct richness modeling
provide some of the best estimates of uncertainty across all modeling
approaches. This highlights the importance of evaluating models based on their
uncertainty as well as their mean estimates (Box 1). Not doing so is
particularly problematic in this case, because the summed species distribution
models are overly confident, which means that these models could mislead
ecologists into believing that richness would be restricted to a much narrower
range than would actually occur.
